Paper_analyses

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
does neutral drive higher pupilary response than negative

>>>>

tmp.df4_full_stim_downs_jun2021_60bins$sample_arousal_lab2<-
  cut(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMeanThisSample, c(-10,-1,1,10), 
                                                              labels = c("low", "mid", "high"))

test<- tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num<500)%>%
  subset(!is.na(ground_arousal_lab))%>%
  # subset(stimIAPS!= "4573")%>%
  # subset(pupil_outlier == FALSE)%>%
  # subset(arousal_outler== FALSE)%>%
  group_by(mediansplit_sample_valence2)%>%
  mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
  ungroup()%>%
  group_by(mediansplit_sample_valence2)%>%
  mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low"))

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num<500)%>%
  subset(!is.na(ground_arousal_lab))%>%
  # subset(stimIAPS!= "4573")%>%
  # subset(pupil_outlier == FALSE)%>%
  # subset(arousal_outler== FALSE)%>%
  # group_by(mediansplit_sample_valence2)%>%
  # mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
  # ungroup()%>%
  # group_by(mediansplit_sample_valence2)%>%
  # mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low")) %>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  # stat_summary(geom = 'pointrange')+
    # facet_grid(~mediansplit_self_valence)

  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
  #              se = F, alpha = .15, size = 1.5)+
  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  # xlim(0,6)+
  facet_grid(~mediansplit_sample_valence2)
# plot separatelly

# negative

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num<500)%>%
  subset(!is.na(ground_arousal_lab))%>%
  subset(mediansplit_sample_valence2 != "More negative")%>%
  mutate(mediantotes = median(arousal, na.rm = TRUE))%>%
  ungroup()%>%
  mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low")) %>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  # stat_smooth(aes(group= stimIAPS), fun = mean,
               # se = F, alpha = .15, size = 1.5)+
  geom_smooth(aes(group = high_lowtes))+
  # stat_smooth(fun = mean,
  #              se = F, alpha = .15, size = 3)+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")
  # xlim(0,6)+
  facet_grid(~ high_lowtes)+
  geom_hline(yintercept = 0)+
  geom_hline(yintercept = -0.5)

# start wit aggregate()

# tmp.df4_full_stim_downs_jun2021_60bins%>%

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num<500)%>%
  subset(!is.na(ground_arousal_lab))%>%
  subset(stimIAPS!= "4573")%>%
  subset(pupil_outlier == FALSE)%>%
  group_by(stimIAPS,stimDescription, mediansplit_sample_arousal2, mediansplit_sample_valence2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
    group_by(mediansplit_sample_valence2)%>%
  mutate(high_lowtes = if_else(arousal> median(arousal, na.rm = TRUE), "high", "low"))%>%
  ggplot(aes(x =high_lowtes , y = pup_basCor))+
  stat_summary(geom = 'pointrange')+
  facet_grid(~mediansplit_sample_valence2)+
  geom_text(aes(label = stimDescription))

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num<500)%>%
  subset(!is.na(ground_arousal_lab))%>%
  subset(stimIAPS!= "4573")%>%
  subset(pupil_outlier == FALSE)%>%
  group_by(stimIAPS,stimDescription, mediansplit_sample_arousal2, mediansplit_sample_valence2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
    group_by(mediansplit_sample_valence2)%>%
  mutate(high_lowtes = if_else(arousal> median(arousal, na.rm = TRUE), "high", "low"))%>%
  ggplot(aes(x =high_lowtes , y = Mean_gray_z))+
  stat_summary(geom = 'pointrange')+
  facet_grid(~mediansplit_sample_valence2)+
  geom_text(aes(label = stimDescription))
    # facet_grid(~mediansplit_self_valence)
  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = median,geom = "line",
               # se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+
  # stat_summary(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), fun = mean, geom = "pointrange")+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
  facet_grid(~mediansplit_self_valence)
